\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-22 tex/methods.tex
use abbreviation for SCCs
clarify acyclicity of SCC graph
consistently use node rather than vertex

Corresponding to the SCC decomposition of $G$ we can construct a directed acyclic graph $\hier (G)$ or the condensed graph \cite{Corominas-Murtra2013}.  Each node of $\hier (G)$ corresponds to a strongly connected component of $G$. There is an edge from the node corresponding to component $C$ to the node corresponding to component $C'$ if and only if there exists a link from some vertex in $C$ to some vertex in $C'$ in $G$.  Because of the maximality of strongly connected components, $\hier (G)$ is acyclic.

>>>>

Corresponding to the SCC decomposition of $G$ we can construct a directed acyclic graph $\hier (G)$ or the condensed graph \cite{Corominas-Murtra2013}.  Each node of $\hier (G)$ corresponds to a SCC of $G$. There is an edge from the node corresponding to component $C$ to the node corresponding to component $C'$ if and only if there exists a link from some node in $C$ to some node in $C'$ in $G$.

### 2015-07-22 tex/overview.tex
consistently use node rather than vertex

\subsection{Abstracting network architectures to their strongly connected components}
We will ultimately find that it is possible to decompose the computation of dynamical robustness from \ref{eq:robustnessfromstoch} over a certain kind of modular structure intrinsic to any network architecture. Here we introduce the manner in which such a decomposition can be consistently performed for any architecture. The network architecture represented in terms of the adjacency matrix, \ref{eq:lininterdepadj}, can be abstracted into modules by decomposing the interaction graph into its associated network of strongly connected components (SCCs). A SCC of a graph is a maximal subset of vertices where each vertex within the subset can be reached from any other in some number (not necessarily single) number of steps \cite{Cormen2009}. The SCCs of some examples of three variable systems are outlined in \reffigscc{} along with their adjacency matrices.

The map from the interaction graph of a network to its SCCs, referred to as $\hier$ in \ref{fig:modsccsym}, results in a decomposition of $G$ into its SCCs. Each node of $\hier (G)$ corresponds to a SCC of $G$. There is an edge from the node corresponding to component $C$ to the node corresponding to component $C'$ if and only if there exists a link from some vertex in $C$ to some vertex in $C'$ in $G$. Note that $\hier (G)$ is acyclic for any $G$ because of the maximality property of SCCs.

One can also perform this construction in the opposite direction to produce one of the graphs consistent with a given specification of SCCs and their connectivity.  Start with a directed acyclic graph $H$.  To each node $n$ of $H$ associate
a strongly connected graph $C_n$.  To each link $(i,j)$ of $H$ associate a non-empty subset of $\Vertex(C_i) \times \Vertex(C_j)$.  The result will be a graph $G$ such that $\hier(G) = H$ and furthermore, every graph $G$ such that $\hier(G) = H$ can be obtained in this manner.

@@

The decomposition of a digraph into SCCs corresponds to a block triangular decomposition of its adjacency matrix.  Say that the graph $G$ has SCCs $C_1, C_2, \ldots C_n$, where we now use $n$ with no index to specify the number of SCCs, which have been labelled in such a way that there are no links from vertices in component $C_i$ to component $C_j$ when $i < j$.  Label the vertices in such a way that $V_1, \ldots, V_{n_1}$ belong to $C_1$, $V_{n_1 + 1}, \ldots, V_{n_2}$ belong to $C_2$, etc.  Then, if we choose basis vectors corresponding to this labelling of the vertices, we will have $a_{ij} = 0$ whenever $i$ and $j$ correspond to different components and $i > j$.  This condition is equivalent to stating that the matrix is block triangular with blocks of size $n_1, n_2, \ldots$.

>>>>

\subsection{Abstracting network architectures to their strongly connected components}
We will ultimately find that it is possible to decompose the computation of dynamical robustness from \ref{eq:robustnessfromstoch} over a certain kind of modular structure intrinsic to any network architecture. Here we introduce the manner in which such a decomposition can be consistently performed for any architecture. The network architecture represented in terms of the adjacency matrix, \ref{eq:lininterdepadj}, can be abstracted into modules by decomposing the interaction graph into its associated network of strongly connected components (SCCs). A SCC of a graph is a maximal subset of nodes where each node within the subset can be reached from any other in some number of (not necessarily single) steps \cite{Cormen2009}. The SCCs of some examples of three variable systems are outlined in \reffigscc{} along with their adjacency matrices.

The map from the interaction graph of a network to its SCCs, referred to as $\hier$ in \ref{fig:modsccsym}, results in a decomposition of $G$ into its SCCs. Each node of $\hier (G)$ corresponds to a SCC of $G$. There is an edge from the node corresponding to component $C$ to the node corresponding to component $C'$ if and only if there exists a link from some node in $C$ to some node in $C'$ in $G$. Note that $\hier (G)$ is acyclic for any $G$ because of the maximality property of SCCs.

One can also perform this construction in the opposite direction to produce one of the graphs consistent with a given specification of SCCs and their connectivity.  Start with a directed acyclic graph $H$.  To each node $n$ of $H$ associate
a strongly connected graph $C_n$.  To each link $(i,j)$ of $H$ associate a non-empty subset of $\Node(C_i) \times \Node(C_j)$.  The result will be a graph $G$ such that $\hier(G) = H$ and furthermore, every graph $G$ such that $\hier(G) = H$ can be obtained in this manner.

@@

The decomposition of a digraph into SCCs corresponds to a block triangular decomposition of its adjacency matrix.  Say that the graph $G$ has SCCs $C_1, C_2, \ldots C_n$, where we now use $n$ with no index to specify the number of SCCs, which have been labelled in such a way that there are no links from nodes in component $C_i$ to component $C_j$ when $i < j$.  Label the nodes in such a way that $V_1, \ldots, V_{n_1}$ belong to $C_1$, $V_{n_1 + 1}, \ldots, V_{n_2}$ belong to $C_2$, etc.  Then, if we choose basis vectors corresponding to this labelling of the nodes, we will have $a_{ij} = 0$ whenever $i$ and $j$ correspond to different components and $i > j$.  This condition is equivalent to stating that the matrix is block triangular with blocks of size $n_1, n_2, \ldots$.
